### 2022-10-14 manuscript.Rmd
Remove Word (.docx) output
Round degrees of freedom (df) in text

output:
  papaja::apa6_pdf:
    latex_engine: xelatex
  papaja::apa6_docx: default

@@

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r filter(anova_table, component == "N400" & effect == "condition")$NumDF`, `r filter(anova_table, component == "N400" & effect == "condition")$DenDF`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.

@@

In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.

In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N400" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "N170" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r filter(contrast_table, component == "P1" & phase == "Post-insight")$df`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.

@@

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N170" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r filter(contrast_table_control, component == "N400" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.

Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.

>>>>

output:
  papaja::apa6_pdf:
    latex_engine: xelatex

@@

Averaged across conditions, P1, N170, and N400 amplitudes differed as a function of the phase of the experiment (pre-insight, insight, or post-insight), all $F$s > `r min(filter(anova_table, effect == "phase")$f_value)`, all $p$s `r print_p(max(filter(anova_table, effect == "phase")$p_value))`.
In addition, N400 amplitudes differed as a function of the condition (semantically informed or naive), averaged across the three phases of the experiment, $F$(`r print_df(filter(anova_table, component == "N400" & effect == "condition")$NumDF)`, `r print_df(filter(anova_table, component == "N400" & effect == "condition")$DenDF)`) = `r filter(anova_table, component == "N400" & effect == "condition")$f_value`, $p$ `r print_p(filter(anova_table, component == "N400" & effect == "condition")$p_value)`.
Crucially, the phase × condition interaction was significant for all three ERP components, all $F$s > `r min(filter(anova_table, effect == "phase:condition")$f_value)`, all $p$s < `r print_p(max(filter(anova_table, effect == "phase:condition")$p_value))`.
To answer our main research question, we decomposed these interactions into simple effects of the semantically informed condition versus the naive condition within each of the three phases of the experiment.

@@

In the insight phase, half of the unfamiliar objects were presented with matching keywords, leading to semantically informed perception, and the other half were presented with non-matching keywords, keeping the perception of the objects semantically naive.
Semantically informed perception in this phase was associated with enlarged (i.e., more negative) amplitudes in the N170 component, $b$ = `r filter(contrast_table, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Insight")$p_value)`, and reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Insight")$p_value)`.
There was no reliable difference between conditions in the P1 component, $b$ = `r filter(contrast_table, component == "P1" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Insight")$p_value)`.

In the post-insight phase, the unfamiliar objects were presented for a third time and without any keywords, mirroring the pre-insight phase.
As in the insight phase, semantically informed perception was associated with reduced (i.e., less negative) amplitudes in the N400 component, $b$ = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N400" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N400" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table, component == "N400" & phase == "Post-insight")$p_value)`, while the effect in the N170 component did not recur, $b$ = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "N170" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "N170" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "N170" & phase == "Post-insight")$p_value)`.
Instead, the P1 component was significantly enlarged (i.e., more positive) in response to objects for which semantically informed perception had taken place, $b$ = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$estimate` µV, $t$(`r print_df(filter(contrast_table, component == "P1" & phase == "Post-insight")$df)`) = `r filter(contrast_table, component == "P1" & phase == "Post-insight")$t_value`, $p_\text{corr}$ = `r print_p(filter(contrast_table, component == "P1" & phase == "Post-insight")$p_value)`.

@@

Second, there is an alternative explanation specifically for the effects observed in the insight phase, when the objects were presented together with matching or non-matching keywords.
Namely, the early difference in the N170 component might in fact not be due to semantic information changing the processing of objects in the semantically informed condition (as we had hypothesized), but rather a mismatch response to the objects in the naive condition.
In this condition, objects were presented with non-matching keywords that led participants to indicate that they did not understand what kind of object they were viewing.
These non-matching keywords might have primed participants to expect a certain set of visual features that did actually not come true once the object was displayed, potentially provoking a fast and strong brain response within the first 200 ms.
However, in a control analysis for this alternative explanation, we could show that the N170 effect in the insight phase does not depend on the naive condition.
For this control analysis, we again used the semantically informed condition as defined above, but contrasted it against a different control condition.
Namely, we used those objects that were presented with matching keywords (as in the semantically informed condition) but for which participants failed to capitalize on the keywords and instead indicated that they still did not know what kind of object they were viewing (a kind of "failed insight").
This was the case for an average of `r mean(objects_per_condition$Exclude_informed)` objects per participant (= `r percent(mean(objects_per_condition$Exclude_informed) / 60, accuracy = 0.1)` of objects presented with matching keywords).
Contrasting the semantically informed condition and the failed insight condition, we again observed an enlarged (i.e., more negative) N170 component during semantically informed perception, $b$ = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N170" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N170" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N170" & phase == "Insight")$p_value)`.
Likewise, the reduction of the N400 was replicated in this control analysis, $b$ = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$estimate` µV, $t$(`r print_df(filter(contrast_table_control, component == "N400" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "N400" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "N400" & phase == "Insight")$p_value)`, as was the late reduction in event-related power ($p_\text{cluster}$ = `r print_p(unique(filter(tfr_clusters, contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < p_cluster)$p_val))`; see Supplementary Figure 1).
This adds credibility to the notion that these effects are specific to those objects for which participants experienced a moment of insight induced by semantic information.

Finally, we had wondered if the reduction in alpha/beta power might merely reflect differences in the timing of motor preparation between conditions, given the well-established link between motor processes and beta power over sensorimotor cortex [@kilavik2013].
To rule this out, we extracted single trial percent signal change based on the distribution of clusters from the permutation tests (time window 600–1,200 ms, frequency range 8–20 Hz, electrodes P3, Pz, P4, PO3, POz, and PO4; see Figures 3 and 4).
We then subjected these to a linear-mixed effects model that controlled for log-transformed reaction time as a covariate of no interest.
This confirmed the significant reduction in alpha/beta power for the semantically informed condition as compared to the naive condition in the insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Insight")$p_value)`, as well as in the post-insight phase, $b$ = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$estimate`%, $t$(`r print_df(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$df)`) = `r filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$t_value`, $p_\text{corr}$ `r print_p(filter(contrast_table_control, component == "alpha_beta" & phase == "Post-insight")$p_value)`.
